### 2014-04-15 paper/tubes.tex
minor updates and a new photo

%In graph theory, a semi-Eulerian graph is one which has exactly two edges of odd degree.  This kind of graph supports an Euler tour: a path that travels every edge exactly once, beginning and ending at the two nodes of odd degree (in this case, the user-selected start and end nodes).  We create a graph based on the user-specified geometry data, with edges for all line segments; then add edges to connect graph components and make graph the semi-Eulerian.  We find an Euler tour on the modified graph, and thicken the path to create pipes.  
Our technique for routing this path is inspired by work in generating continuous line illustrations from images~\cite{Wong-continuousline,Bosch-tsp}.  Our routing problem is a version of the Chinese Postman Problem\footnote{The CPP is also known as the route inspection problem: \url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the user's input graph, much as a postman needs to walk along every road at least once to deliver mail.  In our relaxation, we allow creating new edges (i.e., the postman may jump from building to building in addition to using existing roads).
%
%If path components are disconnected, we create edges that connect them; additionally we can create edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).  
%We offer a short algorithm here, with a more mathematically precise definition and associated proof in supplemental materials appendix.

@@

\section{Fabrication Techniques}
Several pragmatic concerns arise when fabricating models with hollow pipes and cavities on additive manufactuing machines. Pipes will frequently lead to overhangs (where an underlying supporting layer has a smaller footprint than the subsequent layer).
%Beyond design, the tubes must actually be printable to be useful.  
%When geometries contain overhangs, as there may be in designed pipes and cavities, 
To allow overhangs, 3D printers lay down support material that must be later removed from the model.  This removal process can be time-intensive and challenging.  The physical fabrication process used by different machines gives rise to differing strategies for avoiding support material or easing its removal.  We next discuss techniques for fused deposition modeling (FDM) machines, such as the Makerbot\footnote{\url{http://makerbot.com}} and multi-jetting machines such as Objet\footnote{\url{http://stratasys.com}}, as well as powder-based (e.g., ZCorp\footnote{\url{http://3dsystems.com}}) and stereolithography (e.g., Form 1\footnote{\url{http://formlabs.com}}).

>>>>

%In graph theory, a semi-Eulerian graph is one which has exactly two edges of odd degree.  This kind of graph supports an Euler tour: a path that travels every edge exactly once, beginning and ending at the two nodes of odd degree (in this case, the user-selected start and end nodes).  We create a graph based on the user-specified geometry data, with edges for all line segments; then add edges to connect graph components and make graph the semi-Eulerian.  We find an Euler tour on the modified graph, and thicken the path to create pipes.  
Our technique for routing this path is inspired by work in generating continuous line illustrations from images~\cite{Wong-continuousline,Bosch-tsp}.  Our routing problem is a version of the Chinese Postman Problem\footnote{The CPP is also known as the route inspection problem: \url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described by the user's input, much as a postman needs to walk along every road at least once to deliver mail.  In our relaxation, we allow the creation of new edges (i.e., the postman may jump from building to building in addition to using existing roads).
%
%If path components are disconnected, we create edges that connect them; additionally we can create edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).  
%We offer a short algorithm here, with a more mathematically precise definition and associated proof in supplemental materials appendix.

@@

\section{Fabrication Techniques}
Several pragmatic concerns arise when fabricating models with hollow pipes and cavities on additive manufactuing machines. Pipes will frequently lead to overhangs (where an underlying supporting layer has a smaller footprint than the subsequent layer).
%Beyond design, the tubes must actually be printable to be useful.  
%When geometries contain overhangs, as there may be in designed pipes and cavities, 
To allow overhangs, 3D printers lay down support material that must be later removed from the model.  This removal process can be time-intensive and challenging.  The physical fabrication process used by different machines gives rise to differing strategies for avoiding support material or easing its removal.  We next discuss techniques for fused deposition modeling (FDM) machines, such as the Makerbot\footnote{\url{http://makerbot.com}} and multi-jetting machines such as Objet\footnote{\url{http://stratasys.com}}, as well as powder-based machines (e.g., ZCorp\footnote{\url{http://3dsystems.com}}) and those that use stereolithography (e.g., Form 1\footnote{\url{http://formlabs.com}}).
